Philosophy of Distributional Semantics\\ \large Best Practices for the Application of Computational Methods to Questions of Meaning

### 2017-05-23 pds/Paper/pds_references.tex
final commit of the day. sort of an intro
added some flesh to that there bone

%DS Papers

>>>>

@misc{principles,
  title = {{Discrimination algorithms disparate impact} Kernel Description},
  howpublished = {\url{https://www.theatlantic.com/business/archive/2015/09/discrimination-algorithms-disparate-impact/403969/
}},
  note = {Accessed: 2017-05-22}
}

%DS Papers
@article{wagner2015s,
  title={It's a man's wikipedia? Assessing gender inequality in an online encyclopedia},
  author={Wagner, Claudia and Garcia, David and Jadidi, Mohsen and Strohmaier, Markus},
  journal={arXiv preprint arXiv:1501.06307},
  year={2015}
}
@article{harris1954distributional,
  title={Distributional structure},
  author={Harris, Zellig S},
  journal={Word},
  volume={10},
  number={2-3},
  pages={146--162},
  year={1954},
  publisher={Taylor \& Francis}
}
@article{boleda2016formal,
  title={Formal Distributional Semantics: Introduction to the Special Issue},
  author={Boleda, Gemma and Herbelot, Aur{\'e}lie},
  journal={Computational Linguistics},
  year={2016},
  publisher={MIT Press}
}
